---
title: ""
author: "Akash Gupta"
date: "11/3/2018"
output: html_document
---

#Read_Csv
```{r}
sys_admin <-read.csv("SystemAdministrators.csv")
summary(sys_admin)
```

#Loading_Packages
```{r}
library(rmarkdown)
library(ggplot2)
library(caret)
library(gains)
library(tidyverse)
library(knitr)
library(lattice)
```

#Scatter_Plot
```{r}
ggplot(sys_admin, aes(x=Experience, y=Training,color=Completed.task,shape=Completed.task)) +labs(title = "Experience vs Training")+ geom_point()
```
 
 From the Scatter Plot we can infer that Training  has only three possible values which are 4 Credits,6 Credits and 8 Credits.I have used shape to show whether the Task.completed is a "Yes"(Triangle shape) or a "No"(circular).Also I have used different colors for both Yes and No in Completed.task .Since Training has only three possible values namely 4,6 and 8 credits it is not providing much significance in terms of telling whether the task completion was a Yes or No.The major predictor variable here is Experience we can see with the increase in amount of experience in years the Task Completion can be found to be Yes.Therefore Experience is the major predictor variable.

#Running a logistic Regression 
```{r}
logit.reg <- glm(sys_admin$Completed.task ~., data =sys_admin, family = "binomial") 
summary(logit.reg)
pred <- predict(logit.reg,sys_admin, type = "response")#array of predicted values
summary(pred)

```
We can infer by running the logistic regression keeping Completed.task as the outcome variable and using both predictors Experience and Training we can see that only Experience is providing significance.Also from the ggplot we saw that training credits can have only 3 values as given in the dataset and our model shows that whether the task was completed or not depends on Experience accumulated not Training Credits.
As Experience increases the probability for Completing the Task increases therefore we can say that Experience is potentially useful for classifying Task Completion

#Confusion_Matrix
```{r}
confusionMatrix(as.factor(ifelse(pred>0.5,'Yes','No')),(sys_admin$Completed.task))#comparing the actual class with predicted class
```

#Percentage of programmers incorrectly classified as failing to complete the task
```{r}
5/(5+10)*100 #Computing the percentage of programmers incorrectly classified as failing to complete the task 

```
The percentage of programmers that are incorretly classified as failing to complete the task is 33.3333% 


#Years of experience that must be accumulated by a programmer with 6 training
#credits before his or her estimated probability of completing the task exceeds 0.6
```{r}
odds <- log(0.6/(1-0.6))
x1 <- (odds - (0.1805 * 6) + 10.9813)/1.1269
x1

```
Taking log of odds as the Left Hand Side componenet and coeffiecient values from logistic regression output where _0.1805_ is the training credit coefficient and _10.9813_ is the intercept and _1.1269_ is the coefficient for experience.We can see that __9.14346__ years is the amount of experience required to be accumulated by a programmer with 6 training credits before his/her estimated probability of completing the task exceeds _0.6_ .


```
